\begin{landscape}

  \section{Model Comments}

  \subsection{GAM}

  % NOTE: “Misplaced \cr” errors during compilation can be safely ignored.
  \begin{singlespace}
    {\tabulinesep=2mm
      \begin{longtabu}{l L}
        \caption{Comments on GAMs.} \\
        \toprule
        Model name & Comment \\
        \midrule
        \endfirsthead
        Model name & Comment \\
        \midrule
        \endhead
        \bottomrule
        \endlastfoot
        GAM\_gha\_s3SI.h100.diff.EKL.I\_h100.EKL.I &  Spruce: compared to other k-values, lowest GCV score. \\
        GAM\_gha\_s4SI.h100.diff.EKL.I\_h100.EKL.I & Beech: compared to other k-values, lowest GCV score. \\
        GAM\_gha\_s4SI.h100.diff.EKL.I\_s15h100.EKL.I & Beech: compared to other k-values, lowest GCV score. \\
        GAM\_gha\_s5h100 & Beech: compared to other k-values, lowest GCV score. \\
        GAM\_gha\_s6h100 & Spruce: compared to other k-values, lowest GCV score. \\
        GAM\_gha\_s7h100.EKL.I & Beech AND Spruce: compared to other k-values, lowest GCV score. \\
        GAM\_gha\_s7SI.h100.diff.EKL.I\_s15h100.EKL.I & Spruce: compared to other k-values, lowest GCV score.
      \end{longtabu}
    }
  \end{singlespace}
  
  \subsection{SCAM}

  % NOTE: “Misplaced \cr” errors during compilation can be safely ignored.
  \begin{singlespace}
    {\tabulinesep=2mm
      \begin{longtabu}{l L}
        \caption{Comments on SCAMs.} \\
        \toprule
        Model name & Comment \\
        \midrule
        \endfirsthead
        Model name & Comment \\
        \midrule
        \endhead
        \bottomrule
        \endlastfoot
        SCAM\_gha\_mpi4h100.EKL.I & Spruce: smoothest fit compared to other k-values, but also highest GCV score. \\
        SCAM\_gha\_mpi4h100 & Spruce: smoothest fit compared to other k-values, but also highest GCV score. \\
        SCAM\_gha\_mpi4SI.h100.diff.EKL.I\_mpi4h100.EKL.I & Beech AND Spruce: appears to be the smoothest fit, but definitely has the highest GCV score. \\
        SCAM\_gha\_mpi5h100 & Beech: smoothest fit and lowest GCV score compared to other k-values. \\
        SCAM\_gha\_mpi13h100.EKL.I & Spruce: lowest GCV score compared to other k-values. \\
        SCAM\_gha\_mpi13h100 & Spruce: lowest GCV score compared to other k-values. \\
        SCAM\_gha\_mpi14h100.EKL.I & Beech: lowest GCV score compared to other k-values. \\
        SCAM\_gha\_mpi14SI.h100.diff.EKL.I\_mpi9h100.EKL.I & Beech: lowest GCV score compared to other combinations of k-values for both terms. \\
        SCAM\_gha\_mpi15h100.EKL.I & Beech: smoothest fit compared to lower k-values and lowest GCV score compared to higher k-values. \\
        SCAM\_gha\_mpi27SI.h100.diff.EKL.I\_mpi18h100.EKL.I & Spruce: lowest GCV score compared to other combinations of k-values for both terms. \\
        SCAM\_gha\_s0SI.h100.diff.EKL.I\_mpi4h100.EKL.I & Beech: compared to other combinations of k-values, appears to be the smoothest fit. \\
        SCAM\_gha\_s0SI.h100.diff.EKL.I\_s0h100.EKL.I & Beech AND Spruced: compared to other combinations of k-values, appears to be the smoothest fit. \\
        SCAM\_gha\_s3h100.EKL.I & Beech AND Spruce: compared to higher k-values, smoothest fit; compared to lower k-values, same fit. \\
        SCAM\_gha\_s3h100 & Spruce: compared to higher k-values, smoothest fit; compared to lower k-values, same fit. \\
        SCAM\_gha\_s4h100 & Beech: compared to higher k-values, smoothest fit; compared to lower k-values, same fit. \\
        SCAM\_gha\_s4SI.h100.diff.EKL.I\_mpi4h100.EKL.I & Spruce: compared to other combinations of k-values, appears to be the smoothest fit. \\
        SCAM\_gha\_s4SI.h100.diff.EKL.I\_mpi9h100.EKL.I & Beech: lowest GCV score compared to other combinations of k-values for both terms. \\
        SCAM\_gha\_s4SI.h100.diff.EKL.I\_s15h100.EKL.I & Beech: compared to other combinations of k-values, lowest GCV score. \\
        SCAM\_gha\_s5h100 & Beech: compared to other k-values, lowest GCV score. \\
        SCAM\_gha\_s6h100 & Spruce: compared to other k-values, lowest GCV score. \\
        SCAM\_gha\_s7h100.EKL.I & Beech: compared to other k-values, lowest GCV score. \\
        SCAM\_gha\_s7SI.h100.diff.EKL.I\_s15h100.EKL.I & Spruce: compared to other combinations of k-values, lowest GCV score. \\
        SCAM\_gha\_s21SI.h100.diff.EKL.I\_mpi18h100.EKL.I & Spruce: lowest GCV score compared to other combinations of k-values for both terms. \\
        SCAM\_gha\_s28h100.EKL.I & Spruce: compared to other k-values, lowest GCV score. \\
        SCAM\_gha\_sefuminus3SI.h100.diff.EKL.I\_mpi4h100.EKL.I & Beech: compared to other k-values, smoothest fit. \\
        SCAM\_gha\_sefuminus3SI.h100.diff.EKL.I\_mpi9h100.EKL.I & Beech: compared to other k-values, lowest GCV score. \\
        SCAM\_gha\_sefuminus7SI.h100.diff.EKL.I\_mpi4h100.EKL.I & Spruce: compared to other k-values, smoothest fit. \\
        SCAM\_gha\_sefuminus7SI.h100.diff.EKL.I\_mpi14h100.EKL.I & Spruce: compared to other k-values, lowest GCV score. \\
        SCAM\_gha\_SI.h100.diff.EKL.I\_mpi4h100.EKL.I & Spruce: compared to other k-values, smoothest fit. \\
        SCAM\_gha\_SI.h100.diff.EKL.I\_mpi5h100.EKL.I & Beech: compared to other k-values, smoothest fit. \\
        SCAM\_gha\_SI.h100.diff.EKL.I\_mpi9h100.EKL.I & Beech: compared to other k-values, lowest GCV score. \\
        SCAM\_gha\_SI.h100.diff.EKL.I\_mpi14h100.EKL.I & Spruce: compared to other k-values, lowest GCV score.
      \end{longtabu}
    }
  \end{singlespace}

  \subsection{GAMLSS}

  % NOTE: “Misplaced \cr” errors during compilation can be safely ignored.
  \begin{singlespace}
    {\tabulinesep=2mm
      \begin{longtabu}{l L}
        \caption{Comments on GAMLSSs.} \\
        \toprule
        Model name & Comment \\
        \midrule
        \endfirsthead
        Model name & Comment \\
        \midrule
        \endhead
        \bottomrule
        \endlastfoot
        GAMLSS\_gha\_pbm8SI.h100.diff.EKL.I\_pbm4h100.EKL.I & Beech: compared to other combinations of df-values, lowest AIC. \\
        GAMLSS\_gha\_pbm10SI.h100.diff.EKL.I\_pbm1h100.EKL.I & Spruce: compared to other combinations of df-values, lowest AIC. \\
        GAMLSS\_gha\_ps1h100 & Beech AND Spruce: compared to higher df-values, smoothest fit; compared to lower df-values, same fit. Beech: compared to higher df-values, lowest AIC; compared to lower df-values, same AIC. \\
        GAMLSS\_gha\_ps15h100 & Spruce: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_ps7SI.h100.diff.EKL.I\_pbm4h100.EKL.I & Beech: compared to other combinations of df-values, lowest AIC. \\
        GAMLSS\_gha\_ps17SI.h100.diff.EKL.I\_pbm0h100.EKL.I & Spruce: compared to other combinations of df-values, lowest AIC. \\
        GAMLSS\_gha\_ps16SI.h100.diff.EKL.I\_ps19h100.EKL.I & Beech: compared to other combinations of df-values, lowest AIC. \\
        GAMLSS\_gha\_ps17SI.h100.diff.EKL.I\_ps14h100.EKL.I & Spruce: compared to other combinations of df-values, lowest AIC. \\
        GAMLSS\_gha\_sefuminus3SI.h100.diff.EKL.I\_pbm2h100.EKL.I & Beech: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_sefuminus3SI.h100.diff.EKL.I\_pbm3h100.EKL.I & Spruce: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_sefuminus3SI.h100.diff.EKL.I\_ps6h100.EKL.I & Beech: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_sefuminus3SI.h100.diff.EKL.I\_ps13h100.EKL.I & Spruce: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_sefuminus7SI.h100.diff.EKL.I\_pbm2h100.EKL.I & Beech: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_sefuminus7SI.h100.diff.EKL.I\_pbm0h100.EKL.I & Spruce: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_sefuminus7SI.h100.diff.EKL.I\_ps2h100.EKL.I & Beech: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_sefuminus7SI.h100.diff.EKL.I\_ps13h100.EKL.I & Spruce: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_SI.h100.diff.EKL.I\_pbm2h100.EKL.I & Beech: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_SI.h100.diff.EKL.I\_pbm0h100.EKL.I & Spruce: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_SI.h100.diff.EKL.I\_ps2h100.EKL.I & Beech: compared to other df-values, lowest AIC. \\
        GAMLSS\_gha\_SI.h100.diff.EKL.I\_ps13h100.EKL.I & Spruce: compared to other df-values, lowest AIC. \\
      \end{longtabu}
    }
  \end{singlespace}

\end{landscape}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "MasAr_Notes.tex"
%%% End:
